### 2020-04-08 draft.tex
thm poly dir cart equiv
removed cosmos

First, we note that 
$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0\op \circ \sigma) \to \down \xto{\pi} \Set)$$
is the right Kan extension formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Now,
$\Hom_{\Set\op}(S, !_0\op \circ \sigma) \simeq \Hom_{\Set}(!_0 \circ \sigma\op,
S)\op$ over $\down$, which we may see by noting that $(-)\op : {\infty}\Cat \to {\infty}\Cat^{\term{co}}$ is a cosmological equivalence and therefore preserves
comma squares. Furthermore, we have the following equivalence:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12AJCAWwH1gnLnQC+ACgCE-YgAJOAYywAnBfPbYA5rzqcIaUrIDKASj1oQo0uky58hFGQCMVWoxZthfQcLFSZhqbmltYgGNh4BERO5K70zKyIHOxQEADuhFY2EfbRpC7U8R5JnKkZwaKuMFCa8ESgAGbKfEhkIDgQSDEgDHQARjAMAAq2kQ4gyliaABY4IIXuicnYvCGNzauIbR1IAExZIE0tiLvUO4gAzAsJnhpTOmuHG11nnZeVokA
\begin{tikzcd}
{\Hom_{\Set}(!_0 \circ \sigma\op, S)\op} \arrow[d, "\sim"'] \arrow[r] & \down \arrow[d, "\sigma"] \\
{\Hom_{\Set}(!_0, S)\op} \arrow[r]                                    & \down\op                 
\end{tikzcd}
\]
and therefore we may equivalently calculate this limit as 
$$\lim(\Hom_{\Set}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set).$$
This gives us the equivalence between (1) and (5).

@@

\begin{thm}\label{thm:set.poly.cart.equiv.dir.cart}
  There is an equivalence of categories
  $$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
  between the category of polynomial functors and cartesian transformations and
  Dirichlet functors and cartesian transformations. This equivlalence sends
  representables to representables
  $$(-)^N \mapsto N^{(-)}.$$
\end{thm}
\begin{proof}
  \cite[Proposition 3.14]{GambinoKock}.,....
\end{proof}

>>>>

First, we note that 
$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0\op \circ \sigma) \to \down \xto{\pi} \Set)$$
is the right Kan extension formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Now,
$\Hom_{\Set\op}(S, !_0\op \circ \sigma) \simeq \Hom_{\Set}(!_0 \circ \sigma\op,
S)\op$ over $\down$. Furthermore, we have the following equivalence:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12AJCAWwH1gnLnQC+ACgCE-YgAJOAYywAnBfPbYA5rzqcIaUrIDKASj1oQo0uky58hFGQCMVWoxZthfQcLFSZhqbmltYgGNh4BERO5K70zKyIHOxQEADuhFY2EfbRpC7U8R5JnKkZwaKuMFCa8ESgAGbKfEhkIDgQSDEgDHQARjAMAAq2kQ4gyliaABY4IIXuicnYvCGNzauIbR1IAExZIE0tiLvUO4gAzAsJnhpTOmuHG11nnZeVokA
\begin{tikzcd}
{\Hom_{\Set}(!_0 \circ \sigma\op, S)\op} \arrow[d, "\sim"'] \arrow[r] & \down \arrow[d, "\sigma"] \\
{\Hom_{\Set}(!_0, S)\op} \arrow[r]                                    & \down\op                 
\end{tikzcd}
\]
and therefore we may equivalently calculate this limit as 
$$\lim(\Hom_{\Set}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set).$$
This gives us the equivalence between (1) and (5).

@@

\begin{thm}\label{thm:set.poly.cart.equiv.dir.cart}
  There is an equivalence of categories
  $$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
  between the category of polynomial functors and cartesian transformations and
  Dirichlet functors and cartesian transformations. This equivlalence sends
  representables to representables
  $$(-)^N \mapsto N^{(-)}.$$
\end{thm}
\begin{proof}
This follows by composing the equivalence of $\Dir_{\ulcorner}$ with
$\Ha^{\down}$ from Prop
\ref{prop:set.dirichlet.cartesian.iff.bundle.cartesian} with that of
\cite[Proposition 3.14]{GambinoKock}, noting that
$\Set^{\down}_{\ulcorner}$ is the category of $(\ast,\ast)$-polynomials. 
\end{proof}
